---
title: "Assessment V5+ Codebook"
output: html_document
---


```{r, include=F}
devtools::load_all()

knitr::opts_chunk$set(messages = F, warning = F)
```

```{r}
openmindR::assessmentv5_codebook %>%
  knitr::kable()
```


## Q11

Growth Mindset


## Q14 

Affective polarization

Affective polarization is how much people like progressives relative to conservatives. This is computed by taking the absolute value of the difference in liking for progressives minus liking for conservatives. This is similar to Ingroup-Outgroup polarization, but includes all participants -- not just participants identifying as progressive or conservative.

## Q16

Liking for Outgroup

For this analysis, we determined 'outgroup' by matching people's political identity with the survey questions asking how much they liked people with the same and different political identity. Specifically, if someone identified as liberal, their outgroup liking score was how much they liked conservatives. If someone identified as conservative, their outgroup liking score was how much they liked liberals.

## Q17

Ingroup-Outgroup Polarization

Ingroup-Outgroup polarization is how much people like their own group relative to an opposing group. For this analysis, we determined 'ingroup' and 'outgroup' by matching people's political identity with the survey questions asking how much they liked people with the same and different political identity. Specifically, if someone identified as liberal, their ingroup liking score was how much they liked liberals and their outgroup liking score was how much they liked conservatives. If someone identified as conservative, their ingroup liking score was how much they liked conservatives and their outgroup liking score was how much they liked liberals.


## Q18

Intellectual Humility
