---
title: "openmindR"
output: github_document
---

Install package like this:

```{r setup, eval=FALSE}
devtools::install_github("openmindplatform/openmindR")
```

```{r, echo=F}
knitr::opts_chunk$set(message = F, 
                      warning = F)

```


Load package(s):

```{r}
library(openmindR)
library(tidyverse)
```



## OpenMind Cleaning Functions

```{r, echo = F}
library(DBI)
library(magrittr)
library(glue)
library(lubridate)
library(sjmisc)

db_get_data <- function(tbl_dat) {
  con <- dbConnect(RSQLite::SQLite(), "../om_metrics_report/sql_data/omdata.db")

  out <- con %>%
    tbl(tbl_dat) %>%
    collect()

  dbDisconnect(con)

  return(out)
}


## Matching string for all Q variables
q_strings <- paste0(
  paste0("Q", 1:18, "P", collapse = "|"), "|", paste0("Q", 1:18, "F", collapse = "|")
  )
## Matching string for all (relevant) D variables
d_strings <- paste0("D", 1, collapse = "|")
## Matching string for all C variables
c_strings <- paste0("C", 1:3, collapse = "|")

## Matching string for all (relevant) D, Q and C variables
var_strings <- paste0(q_strings, "|", d_strings, "|", c_strings, collapse = "|")
## Matching string for all Q and C variables
q_c_strings <- paste0(q_strings, "|", c_strings, collapse = "|")
## Matching string for ranging vars from 0 to 1 
range01_strings <- str_c(str_c("Q", 3:12, "P", collapse = "|"), "|",
                         str_c("Q", 3:12, "F", collapse = "|"), 
                         str_c("|", c_strings, collapse = "|")
)


# Read in data
dat.acc <- db_get_data("dat.acc")
dat.par <- db_get_data("dat.par")
dat.ass4 <- db_get_data("dat.ass4")
dat.ass5 <- db_get_data("dat.ass5")

dat.ass <- dat.ass4 %>% 
  rename_at(vars(matches("Followup")), ~str_replace(., "Followup", "FollowUp")) %>%
  bind_rows(dat.ass5)


```


## `om_filter_data`

Filter down Assessment data from AirTable by `AssessmentsDone`, `AssessmentVersion` and `AccessCodes`.

```{r}

dat.ass %>% 
  # specify which number of assessment you want to have
  om_filter_data(n_assessments = 1:3,
             # assessment version?
             version = 4,
             # select Accesscode(s) to produce report for
             accesscode = "Wilkes"
             # "Wilkes" #try this out :)
  )
```

This dataset was filtered down to only AccessCodes that include "Wilkes". The `accesscode` argument is not case-sensitive and can both be used with vectors:

```{r}
dat.ass %>% 
  # specify which number of assessment you want to have
  om_filter_data(n_assessments = 1:3,
             # assessment version?
             version = 4,
             # select Accesscode(s) to produce report for
             accesscode = c("SuszkoWilkesUF18", "KarimiWilkesUF18")
  )
```

And individual strings:

```{r}
dat.ass %>% 
  # specify which number of assessment you want to have
  om_filter_data(n_assessments = 1:3,
             # assessment version?
             version = 4,
             # select Accesscode(s) to produce report for
             accesscode = c("suszko|karimi")
  )
```


## `om_clean_par`

Cleans up ParticipantProgress data and creates several measures:

+ **StepTimes1 to StepTimes5:** Duration in minutes to complete a step

+ **StepCorrect1 to StepCorrect5:** Percentage of correct answers for each step

+ **FeedbackAnswers:** Q1 to Q5 for each individual step

```{r}
dat.par %>% 
  om_clean_par()
```

## `om_construct_measures`

This is a higher-level function that uses both `polar_measures` and `calc_ih` to constuct various measures.

Creates the following variables:

+ **Q14:** Affective Polarization
+ **Q15:** Ingroup
+ **Q16:** Outgroup
+ **Q17:** Ingroup vs. Outgroup Affective Polarization
+ **Q18:** Intellectual Humility

Function automatically accounts for Assessment Version 4 and 5/5.1.


```{r, eval=F}
dat.ass %>% 
  om_construct_measures()
```

> Error in polar_measures(., Q1Pre, Q2Pre) : Input data is missing column `ppol_cat`. Please make sure to run om_clean_ppol before you run om_construct_measures.

Uh oh! That didn't work! `om_construct_measures` needs the column `ppol_cat` to run which can be created with the function `om_clean_ppol`.


## `om_clean_ppol`

Creates the following measures of Political Orientation

+ **ppol_raw:** a variable that merges Assessment V4 and V5.1 spelling of Political Orientation (D4)
+ **ppol:** a factor variable ordered from "Very Progressive/left" to "Very Conservative/right". Excludes all other categories as NA (classical liberal etc.)
+ **ppol_num:** numeric variable ranging from 1 "Very Progressive/left" to 7 "Very Conservative/right"
+ **ppol_cat:** a factor variable which has two categories "Progressive" and "Conservative". The rest is NA.

```{r}

dat.ass <- dat.ass %>% 
  om_clean_ppol()

dat.ass
```

Now `om_construct_measures` will work!

```{r}
dat.ass %>% 
  om_construct_measures()
```

## `remove_dups`

This function is really important to clean up duplicated OMIDs that occasionally occur within AirTable. 

```{r, message = T}
dat.ass %>% 
  remove_dups()
```


## `om_gather`

This function will turn Assessment data into long format.
 
Creates the following variables:

+ **Question:** Q1Pre, Q2Pre, Q3Pre etc.
+ **Type:** Pre, Post, or FollowUp
+ **Response:** Values of the Question
+ **variable_code:** Q1, Q2, Q3 etc.
 
Takes the following arguments:

+ **.data** Assessment data
+ **which_strings** a string indicating which variables should be parsed out (`q_c_strings` indicates all Q and C questions)


```{r}
dat.ass %>% 
  om_gather(q_c_strings) %>% 
  ## select just the relevant vars as showcase
  select(Question, Response, Type, variable_code)
```

## `om_summarize_comparisons`

This is a higher-level function that uses both "bind_questions" and "summarize_comparison" to calculate t-tests and Cohen's d on Assessment data.

```{r}
gathered_dat <- dat.ass %>% 
  om_construct_measures() %>%
  remove_dups() %>%  
  om_gather(q_c_strings) 

gathered_dat %>% #count(variable_code)
  om_summarize_comparisons()
```


## OpenMind ggplot2 theme

There are three functions for the ggplot2 theme:

+ `theme_om`
+ `scale_fill_om`
+ `scale_color_om`

Make sure you have the Poppins font installed!

```{r}
windowsFonts(`Poppins` = windowsFont("Poppins"))

```


[Good tutorial on how to install custom fonts in R](https://www.andrewheiss.com/blog/2017/09/27/working-with-r-cairo-graphics-custom-fonts-and-ggplot/)

**Example**

```{r fig.width=8, fig.height=5, message=F, warning=F}
## Load tidyverse
library(tidyverse)

titanic_dat <- Titanic %>% as_tibble()

titanic_dat %>% 
  ggplot(aes(Sex, n)) +
  geom_col(aes(fill = Class), position = position_dodge()) +
  theme_om(legend_position = c(0.9, 0.75)) +
  scale_fill_om("Class") +
  facet_wrap(~Survived) +
  labs(title = "Titanic Survival by Age and Class") 
  
```

**Adapt `theme_om`**

+ `legend_position`
+ `axis_text_size`
+ `axis_title_size`
+ `legend_text_size`
+ `title_size`

```{r fig.width=8, fig.height=5, message=F}
titanic_dat %>% 
  ggplot(aes(Class, n, fill = Class)) +
  geom_col() +
  theme_om(legend_position = "bottom",
           axis_text_size = 10,
           axis_title_size = 15, 
           legend_text_size = 10,
           title_size = 20) +
  scale_fill_om() +
  facet_wrap(~Survived) +
  labs(title = "Titanic Survival by Class") 
```

Or all text sizes at once

+ `overall_text_size`

```{r fig.width=8, fig.height=5, message=F}
titanic_dat %>% 
  ggplot(aes(Class, n, fill = Class)) +
  geom_col() +
  theme_om(legend_position = "top",
           overall_text_size = 15) +
  scale_fill_om() +
  facet_wrap(~Survived) +
  labs(title = "Titanic Survival by Class") 
```


