---
title: "openmindR"
output: github_document
---

**Overview**

+ [openmindR Cleaning Functions](https://github.com/openmindplatform/openmindR#openmindr-cleaning-functions)
+ [openmindR Analysis Functions](https://github.com/openmindplatform/openmindR#openmindr-analysis-functions)
+ [openmindR ggplot2 theme](https://github.com/openmindplatform/openmindR#openmindr-ggplot2-theme)

Install package like this:

```{r setup, eval=FALSE}
devtools::install_github("openmindplatform/openmindR")


```





```{r, echo=F}
knitr::opts_chunk$set(message = F, 
                      warning = F, 
                      eval = F)

# key <- readr::read_lines("../../Keys/airtabler.txt")


ups <- c("GrowthMindset", "CIHS_LIO",
         "OutgroupLiking", "OutgroupMotivation",
         "Preparedness", "C1", "C6",
         "IntellectualHumility", "GM", 
         "IHSub1", "IHSub2", "IHSub3",
         "IHCultureSub1", "IHCultureSub2", "IHCultureSub3", 
         "SE", "Belong", "Dissent", "Tolerance", 
         "IngroupLiking", "IngroupMotivation",
          "OutgroupLiking", "OutgroupMotivation", 
         "MotivationCon", "MotivationProg")

downs <- c("AffPol1", "AffPol2",
           "GBSS", "MAA", "C5", 
           "Anxiety", "Attribution", 
           "IntAnx", "SocialDistance", 
           "Avoidance")
# AssessmentV6Codebook <- readRDS("data/AssessmentV6Codebook.RDS")
# 
# usethis::use_data(AssessmentV6Codebook)
# 
# AssessmentV7Codebook <- readRDS("../../Research/Assessments & Codebooks/v7/AssessmentV7Codebook/data/AssessmentV7Codebook.RDS")
# 
# usethis::use_data(AssessmentV7Codebook)



# v6_var_strings <- "AffPol1|AffPol2|OutgroupLiking|IngroupLiking|MotivationProg|MotivationCon|CIHS_LIO|GrowthMindset|GBSS|MAA|OutgroupMotivation|IngroupMotivation|Preparedness|C1|C5|C6|IntellectualHumility|SoughtOutDifferent"
# 
# usethis::use_data(v6_var_strings, overwrite = T)
```


Load package(s):

```{r, eval = T}
library(openmindR)
library(tidyverse)

```

# Create Master dataset

This code merges Assessment data with Participant Progress and Access Codes tables (to add UserType, OpenMindVersion and other variables).

```{r}
pacman::p_load(tidyverse, openmindR)


assessmentv6 <- om_download_at(tables = "AssessmentV6",
                               clean = T, v6.1 = T)

## ParticipantProgress1
pp1 <- om_download_at(tables = "ParticipantProgress") %>% 
  select(OMID, AccessCode, OpenMindVersion, Country, 
         Research, DateStarted, DateFinished)

## ParticipantProgress2
pp2 <- om_download_at(tables = "ParticipantProgress2") %>% 
  select(OMID, AccessCode, OpenMindVersion, Country, 
         Research, DateStarted, DateFinished)

## AccessCodes
acs <- om_download_at(tables = "AccessCodes") %>%
  select(AccessCode, UserType, GroupName)

## bring it all together
cleaned_dat <- pp1  %>%
  bind_rows(pp2) %>%
  ## turn dates into date format
  mutate(DateFinished = lubridate::as_date(DateFinished)) %>%
  mutate(DateStarted = lubridate::as_date(DateStarted)) %>%
  ## compute WithinADay
  mutate(WithinADay = as.numeric(DateStarted==DateFinished)) %>%
  ## join in Assessment data
  coalesce_join(assessmentv6, join = dplyr::right_join) %>% 
  ## join in Access Code Data
  coalesce_join(acs, join = dplyr::left_join) %>%
  ## if AccessCode is IndividualUser, then UserType is IndividualUser
  mutate(UserType = ifelse(AccessCode == "IndividualUser",
                           "IndividualUser", UserType)) %>%
  drop_na(UserType) %>%
  drop_na(DateStarted)




```

```{r, eval = F, echo = F}
pacman::p_load(tidyverse, openmindR)

  # AssessmentV7 <- airtabler::airtable(om_base, "AssessmentV7Copy")$AssessmentV7Copy$select_all() %>% 
  # janitor::remove_empty()


assessmentv7 <- om_download_at(tables = "AssessmentV7",
                               clean = T, v6.1 = T) %>% 
  janitor::remove_empty()
  # mutate(DateStarted = lubridate::as_date(DateStarted)) %>% 
  # mutate(DateFinished = lubridate::as_date(DateFinished))

## ParticipantProgress1
pp1 <- om_download_at(tables = "ParticipantProgress") %>% 
  select(OMID, AccessCode, OpenMindVersion, Country, 
         Research, DateStarted, DateFinished, StepsComplete, StepScores) %>%
  mutate(ModsCompleteN = str_count(StepsComplete, "1")) %>% 
  mutate(QScore = StepScores %>% map_dbl(~{.x %>% 
      str_split(",") %>% 
      unlist %>% 
      parse_number %>% 
      sum(na.rm = T) %>% 
      magrittr::divide_by(33) %>% 
      magrittr::multiply_by(100)
    }
    )) %>% 
  select(-StepsComplete, -StepScores)

## ParticipantProgress2
pp2 <- om_download_at(tables = "ParticipantProgress2") %>% 
  select(OMID, AccessCode, OpenMindVersion, Country, 
         Research, DateStarted, DateFinished, ModsComplete, ModScores) %>%
  mutate(ModsCompleteN = str_count(ModsComplete, ",") + 1) %>% 
  mutate(QScore = ModScores %>% map_dbl(~{.x %>% 
      str_split(",") %>% 
      unlist %>% 
      parse_number %>% 
      sum(na.rm = T) %>% 
      magrittr::divide_by(33) %>% 
      magrittr::multiply_by(100)
    }
    )) %>% 
  select(-ModsComplete, -ModScores)




str_split(pp2$ModScores, ",") %>% 
  map(unlist)

## AccessCodes
acs <- om_download_at(tables = "AccessCodes") %>%
  select(AccessCode, UserType, GroupName)

## bring it all together
cleaned_dat <- pp1   %>% 
  bind_rows(pp2) %>%
  ## turn dates into date format
  mutate(DateFinished = lubridate::as_datetime(DateFinished)) %>%
  mutate(DateStarted = lubridate::as_datetime(DateStarted)) %>%
  ## compute WithinADay
  mutate(WithinADay = as.numeric(DateStarted==DateFinished)) %>%
  ## join in Access Code Data
  coalesce_join(acs, join = dplyr::left_join) %>%
  ## join in Assessment data
  coalesce_join(assessmentv7, join = dplyr::right_join) %>% 
  ## if AccessCode is IndividualUser, then UserType is IndividualUser
  # mutate(UserType = ifelse(AccessCode == "IndividualUser",
                           # "IndividualUser", UserType)) %>%
  mutate(Research = ifelse(is.na(Research), "No", Research)) %>% 
  drop_na(UserType) %>%
  drop_na(DateStarted)

# cleaned_dat %>% View()
# 
# assessmentv7$DateStarted

om_base <- "appjU7KUyybZ4rGvT"


cleaned_dat %>% 
  split(1:nrow(.)) %>% 
      map(
        ~{
          airtabler::air_update(om_base, "AssessmentV7Copy", record_id = .x$id, record_data = .x %>% select(OpenMindVersion, UserType, Country, Research, ModsCompleteN, QScore, DateStarted, DateFinished) %>% as.list())
        }
      )    

assessmentv7 %>% select(sex_nonstraight) %>% count(sex_nonstraight)

assessmentv7 %>% select(WithinADay) %>% count(WithinADay)

assessmentv7 %>% select(ut_college_individ) %>% count(ut_college_individ)


assessmentv7 %>%
  select(OMID, AccessCode, UserType:Research) %>%
  filter(is.na(OpenMindVersion))
```


# openmindR Cleaning Functions

The following functions are meant to turn AirTable data into a single clean file that can be analyzed.

+ [om_download_at](https://github.com/openmindplatform/openmindR#om_download_at)

+ [om_filter_data](https://github.com/openmindplatform/openmindR#om_filter_data)
+ [om_clean_ppol](https://github.com/openmindplatform/openmindR#om_clean_ppol)
+ [om_dummy_nonwhite](https://github.com/openmindplatform/openmindR#om_dummy_nonwhite)
+ [om_dummy_nonstraight](https://github.com/openmindplatform/openmindR#om_dummy_nonstraight)
+ [om_gather](https://github.com/openmindplatform/openmindR#om_gather)
+ [om_parse_lifehacks](https://github.com/openmindplatform/openmindR#om_parse_lifehacks)
+ [merge_assessments](https://github.com/openmindplatform/openmindR#merge_assessments)



```{r, echo = F, eval=T}

db_get_data <- function(tbl_dat) {
  con <- DBI::dbConnect(RSQLite::SQLite(), "../../Research/Projects/Current Projects/om_metrics_report/sql_data/omdata.db")

  out <- con %>%
    dplyr::tbl(tbl_dat) %>%
    dplyr::collect()

  DBI::dbDisconnect(con)

  return(out)
}


# Matching string for all Q variables
# q_strings <- paste0(
#   paste0("Q", 1:18, "P", collapse = "|"), "|", paste0("Q", 1:18, "F", collapse = "|")
#   )
# ## Matching string for all (relevant) D variables
# d_strings <- paste0("D", 1, collapse = "|")
# ## Matching string for all C variables
# c_strings <- paste0("C", 1:3, collapse = "|")
# 
# ## Matching string for all (relevant) D, Q and C variables
# var_strings <- paste0(q_strings, "|", d_strings, "|", c_strings, collapse = "|")
# ## Matching string for all Q and C variables
# q_c_strings <- paste0(q_strings, "|", c_strings, collapse = "|")
# ## Matching string for ranging vars from 0 to 1
# range01_strings <- stringr::str_c(stringr::str_c("Q", 3:12, "P", collapse = "|"), "|",
#                          stringr::str_c("Q", 3:12, "F", collapse = "|"),
#                          stringr::str_c("|", c_strings, collapse = "|")
# )


# Read in data
# dat.acc <- db_get_data("dat.acc")
# dat.par <- db_get_data("dat.par")
# # dat.ass4 <- db_get_data("dat.ass4")
# # dat.ass5 <- db_get_data("dat.ass5")
# # dat.ass <- db_get_data("cleaned_dat")
# 
# dat.ass <- readr::read_csv("../../Research/Data/2019-10-29_assessmentv4.csv") %>% 
#   dplyr::bind_rows(readr::read_csv("../../Research/Data/2019-10-29_assessmentv5.csv"))


# dat.ass <- dat.ass4 %>% 
#   dplyr::rename_at(dplyr::vars(dplyr::matches("Followup")), ~stringr::str_replace(., "Followup", "FollowUp")) %>%
#   mutate(OMID = as.character(OMID)) %>% 
#   dplyr::bind_rows(dat.ass5 %>% 
#                      mutate(AssessmentVersion = as.numeric(AssessmentVersion)) %>% 
#                      mutate(AssessmentsDone = as.numeric(AssessmentsDone)))


```

## `om_download_at`

`openmindR` can download and clean data directly from Airtable. 

+ `clean`: Whether to return "clean" data (i.e. numeric data is numeric and minors or opt-outs are `NA`. Also constructs measures and computes dummy variables. (`TRUE`/`FALSE`)
+ `file`: give a file path to where the downloaded data should be stored
+ `v6.1`: filter down the dataset to only include Assessment V6.1 (`TRUE/FALSE`)

Here is a code example that will download Assessment V6, clean it, save it into a folder called "Data" under Research and filter down to only include V6.1 data.


```{r, eval=F}


assessmentv6 <- om_download_at(
                            tables = "AssessmentV6", 
                            clean = TRUE, 
                            file = "../../../Data/assessmentv6.1.csv",
                            v6.1 = TRUE)


```

Here is another example code for downloading a clean version of Assessment v7:

```{r, eval=T}

assessmentv7 <- om_download_at(
                            tables = "AssessmentV7", 
                            clean = TRUE)


```

## `om_filter_data`

Filter down Assessment data from AirTable by `AssessmentsDone`, `AssessmentVersion` and `AccessCodes`.

```{r}

assessmentv7 %>% 
  # specify which number of assessment you want to have
  om_filter_data(n_assessments = 1:2,
             # assessment version?
             version = 7,
             # select Accesscode(s) 
             accesscode = "TuttlePen"
             # "TuttlePen" #try this out :)
  )
```

The `accesscode` argument is not case-sensitive and can both be used with vectors:

```{r}
assessmentv7 %>% 
  # specify which number of assessment you want to have
  om_filter_data(n_assessments = 1:2,
             # assessment version?
             version = 7,
             # select Accesscode(s) 
             accesscode = c("TuttlePennStateS20", "SpriggsBTHS201S20")
  )
```

And individual strings:

```{r}
assessmentv7 %>% 
  # specify which number of assessment you want to have
  om_filter_data(n_assessments = 1:2,
             # assessment version?
             version = 7,
             # select Accesscode(s) to produce report for
             accesscode = c("tuttle|spriggs")
  )
```





## `om_clean_ppol`

Creates the following measures of Political Orientation

+ **ppol_raw:** a variable that has all political orientation variables across all Assessment Versions (corresponds to `D4`)
+ **ppol:** a factor variable ordered from "Very Progressive/left" to "Very Conservative/right". Excludes all other categories as NA (classical liberal etc.)
+ **ppol_num:** numeric variable ranging from 1 "Very Progressive/left" to 7 "Very Conservative/right"
+ **ppol_extreme:** numeric variable ranging from 0 "Moderate/Middle-of-the-road" to 3 "Very Conservative/right" or "Very Progressive/left"
+ **ppol_cat:** a factor variable which has two categories "Progressive" and "Conservative". The rest is NA.
+ **ppol_catmod:** a factor variable which has three categories "Progressive", "Conservative" and "Moderates". The rest is NA.


```{r, eval = F}
assessmentv7 %>% 
  om_clean_ppol()
```

## `om_dummy_nonwhite`

This function creates a dummy variable from D3 (Race) called `race_nonwhite` and codes people who identify **only** as white as 0 and everyone else as 1.

```{r, eval = F}
assessmentv7 %>% 
  om_dummy_nonwhite()
```

## `om_dummy_nonstraight`

This function creates a dummy variable from D5 (Sexuality) called `sex_nonstraight` and codes people who identify as heterosexual as 0 and everyone else as 1.

```{r, eval = F}
assessmentv7 %>% 
  om_dummy_nonstraight()
```

## `om_dummy_ut`

This function creates the dummy variables from UserType

+ `ut_college_individ`: College student (0) v. individual user (1)
+ `ut_corp_individ`: Corp (0) v. individual user (1)
+ `ut_college_corp`: College student (0) v. corp (1)


```{r, eval = F}
assessmentv7 %>% 
  om_dummy_ut()
```


## `om_gather`

This function will turn Assessment data into long format.
 
Creates the following variables:

+ **Question:** Q1Pre, Q2Pre, Q3Pre etc.
+ **Type:** Pre, Post, or FollowUp
+ **Response:** Values of the Question
+ **variable_code:** Q1, Q2, Q3 etc.
 
Takes the following arguments:

+ **.data** Assessment data
+ **which_strings** a string indicating which variables should be parsed out (`v7_var_strings` has all variables for v7). The format looks as follows: "AffPol1|AffPol2|GM1" (so each variable without the "Pre", "Post" or "FollowUp" suffix)


```{r, eval = F}
assessmentv7 %>% 
  om_gather(v7_var_strings) %>% 
  ## select just the relevant vars as showcase
  select(Question, Response, Type, variable_code)
```

## `om_parse_lifehacks`


This function parses and cleans the list variables that contain the lifehack data. The input dataset needs to have the four following columns: `LifeHacksChosen`, `LifeHacksComplete`, `LifeHacksUseful` and `LifeHacksReason`. You can find them in the ParticipantProgress table in Airtable. The function will parse these four columns into 4 x 5 Steps variables (so 20 in total):

+ `LifeHack1` - `LifeHack5`: Which Lifehack was chosen
+ `LifeHacksComplete1` - `LifeHacksComplete5`: Did the user complete the lifehack
+ `LifeHacksUseful1` - `LifeHacksUseful5`: Did the user find completing the lifehack useful
+ `LifeHacksReason1` - `LifeHacksReason5`: Why didn't the user complete the lifehack

```{r, eval = F}
## get key
key <- read_lines("../../Keys/airtabler.txt")

## download participant progress data
pp_dat <- om_download_at(tables = "ParticipantProgress")


## this parses all Lifehack data so far
parsed_lh <-  om_parse_lifehacks(pp_dat)


## if you just want the newest life hack data you can filter by OpenMind version
parsed_lh <-  pp_dat %>%
  ## making sure OpenMindVersion is numeric
  mutate(OpenMindVersion = as.numeric(OpenMindVersion)) %>% 
  ## Only include OM Version 3 and above
  filter(OpenMindVersion >= 3) %>% 
  ## parse Life hacks
  om_parse_lifehacks()

## just select the OMID and all LifeHack data (remove all other PP variables)
parsed_lh %>% 
  select(OMID, LifeHack1:LifeHacksReason5)
```


## `merge_assessments`

This function merges assessment v4, v5 and v6 data and only keeps common variables. 

```{r, eval= F}
## get previous assessment dat
v4 <- read.csv("../../../Data/2019-10-29_assessmentv4.csv") 
v5 <- read.csv("../../../Data/2019-10-29_assessmentv5.csv") 


## get (clean) assessment v6 data
v6 <- om_download_at(tables = "AssessmentV6", clean = T)


## merge all three datasets and only keep common variables
merge_assessments(v4, v5, v6)

```


## `om_reverse_code`

Reverse codes items and adds them at the end of the dataset with a "`*_Rev`" at the end.

```{r, eval = F}
assessmentv7 %>% 
  om_reverse_code()
```


# openmindR Analysis Functions

This section introduces the openmindR analysis functions.

+ [om_ttest](https://github.com/openmindplatform/openmindR#om_ttest)
+ [om_lm](https://github.com/openmindplatform/openmindR#om_lm)
+ [om_lmer](https://github.com/openmindplatform/openmindR#om_lmer)
+ [om_textscore](https://github.com/openmindplatform/openmindR#om_textscore)


## `om_ttest`

This function performs paired t-tests on long format Pre-Post-FollowUp data and returns stats on the model (including p-values, t-statistics and Cohen's D effect size).

`om_ttest` takes two arguments:

+ `gathered_dat` OpenMind data in long format (must be created with [om_gather](https://github.com/openmindplatform/openmindR#om_gather))
+ `comparison` Three possible comparisons "PrePost", "PreFollowUpT1T2" or "PreFollowUpT1T3"

PreFollowUpT1T2 performs Pre-Post comparison only for people who completed the FollowUp. PreFollowUpT1T3 is the same sample of people (only those who completed the FollowUp) but compares them Pre-FollowUp. 
    
First we download v7 data:

```{r, eval = F}

## Get Key (may differ in your code)


## get v7 data
assessmentv7 <- om_download_at(key,
                            tables = "AssessmentV7",
                            clean = TRUE)

```

You can perform t-tests on a single variable by *only* gathering one variable and specifying the comparison (here: `"PrePost"`).  

```{r}
## Perform t-test on a single variable
assessmentv7 %>% 
  om_gather("AffPol1") %>% 
  om_ttest(comparison = "PrePost")
```

However, this is not how `om_ttest` is intended to work. Rather it should be used on a dataset in long format with all variables that you want to perform analysis on. The next lines of code show that process. 

```{r}
## get results for all variables
assessmentv7  %>%
  ## select only relevant variables and composite scores
  select(OMID, AffPol1Pre:IHCultureSub3FollowUp) %>% 
  ## turn data into long format
  om_gather(which_strings = v7_var_strings)  %>%
  ## perform t-test on each variable (for Pre and Post)
  om_ttest("PrePost") %>% 
  ## arrange by cohens D
  arrange(desc(cohend)) 


```

Same process for Assessment v6:

```{r}
## get results for all variables
assessmentv6  %>%
  ## select only relevant variables and composite scores
  select(OMID, AffPol1Pre:IntellectualHumilityFollowUp, 
         GrowthMindsetPre, GrowthMindsetPost, GrowthMindsetFollowUp,
         C1Pre, C5Pre, C6Pre, 
         C1Post, C5Post, C6Post,
         C1FollowUp, C5FollowUp, C6FollowUp,
         -contains("Preparedness3")) %>% 
  ## turn data into long format
  om_gather(which_strings = v6_var_strings)  %>%
  ## perform t-test on each variable (for Pre and Post)
  om_ttest("PrePost") %>% 
  ## arrange by cohens D
  arrange(desc(cohend)) 


```

### `perc_improved`

`om_ttest` uses a helper function to determine the percentage of people who improved: `perc_improved` from T1 to T2 (or T3). For this, we need to decide which variables are coded so that "improvement" means higher values and which ones coded so that improving means lower values on the respective scales.

Here is the list of variables that should have **higher values** to show improvement:

```{r, echo = F, eval = T}
ups #%>% 
  # paste0(collapse = "<br>") %>% 
  # htmltools::HTML()
```

Here is the list of variables that should have **lower values** to show improvement:

```{r, echo = F, eval = T}
downs #%>% 
  # paste0(collapse = "<br>") %>% 
  # htmltools::HTML()
```

## `om_lm`

Run linear regression model (with interactions)

This function performs linear regression and gives back some neat info

Four inputs:

+ *.data* data that was used to fit the model

+ *lin_mod* a fitted model

+ *type* what kind of model (currently only accepts `"int"` for interactions)

+ *switch* logical. Switch variables in interaction plot. Default is `FALSE`

```{r, eval = T}
mod1 <- lm(ppol_extreme ~ ppol_cat*gender, 
           data = assessmentv7)


results <- assessmentv7 %>% 
  om_lm(lin_mod = mod1, 
        type = "int",
        switch = T)


```

The function returns 5 outputs (in list format).

```{r}
results$model
results$table
results$estimated_means
results$plot
results$report
```


### Show the model

```{r, eval = T}
results$model
```

### Show a regression table

```{r, eval = T}

results$table
```

### Show an interpretation of the model

```{r, eval = T, results='asis'}

results$report %>% 
  cat()

```

### Show estimated means

```{r, eval = T}

results$estimated_means %>% 
  knitr::kable()
```

### Show a plot of the means

```{r, eval = T}
results$plot  +
  ylab("Political Extremity")
```

### Interaction with Numeric variables

When interacting a numeric with a factor variable, the function will return the mean as well as one SD below/above the numeric response.

```{r, eval = T}
mod1 <- lm(ppol_extreme ~ ppol_cat*AffPol1Pre, 
           data = assessmentv7)


results <- assessmentv7 %>% 
  om_lm(lin_mod = mod1, 
        type = "int",
        switch = F)

results$plot +
  ylab("Political Extremity")
```

When both interaction variables are numeric, the function will return the mean as well as one SD below/above for both numeric responsse.

```{r, eval = T, fig.width = 15, height = 5}
mod1 <- lm(ppol_extreme ~ GMPre*AffPol1Pre, 
           data = assessmentv7)


results <- assessmentv7 %>% 
  om_lm(lin_mod = mod1, 
        type = "int",
        switch = T)

results$plot +
  ylab("Political Extremity")
```

## `om_lmer`

Run mixed models (with interactions)

This function performs a mixed model and gives back some neat info

Three inputs:


+ *mod* a fitted model

+ *type* what kind of model (currently only accepts `"int"` for interactions)

+ *mod_transform* Indicates which values of the moderator variable should be used when plotting interaction terms (i.e. `type = "int"`). 
   + `"minmax"` (default) minimum and maximum values (lower and
   upper bounds) of the moderator are used to plot the interaction between
   independent variable and moderator(s).} 
   + `"meansd"` uses the mean value of the moderator as well as one standard deviation below and
   above mean value to plot the effect of the moderator on the independent
   variable (following the convention suggested by Cohen and Cohen and
   popularized by Aiken and West (1991), i.e. using the mean, the value one
   standard deviation above, and the value one standard deviation below the
   mean as values of the moderator.
   + `"zeromax"`  is similar to the `"minmax"` option, however,
   `0` is always used as minimum value for the moderator. This may be
   useful for predictors that don't have an empirical zero-value, but absence
   of moderation should be simulated by using 0 as minimum.
   `"quart"` calculates and uses the quartiles (lower, median and
   upper) of the moderator value.
   + `"all"` uses all values of the moderator variable.
   
   
First you need to fit to bring the data into long format and fit the model.
   
```{r, eval = T}
cleaned_dat_long <- openmindR::om_gather(assessmentv7, which_strings = "AffPol1")

mixed <- lme4::lmer(Response~Time * gender + (1|OMID), data = cleaned_dat_long)
```
  
  
Next you can use `om_lmer`.

```{r, eval = T}
results <- om_lmer(mixed,
                   type = "int")

```



### Show the model

```{r, eval = T}
results$model
```

### Show a regression table

```{r, eval = T}

results$table
```

### Show an interpretation of the model

```{r, eval = T, results='asis'}

results$report %>% 
  cat()

```

### Show estimated means

```{r, eval = T}

results$estimated_means %>% 
  knitr::kable()
```

### Show a plot of the means

```{r, eval = T}
results$plot  +
  ggplot2::ylab("Affective Polarization") +
  ggplot2::ylim(0, 50)
```

## `om_textscore`

This function performs sentiment analysis and other methods from different text tools on any dataset with a text colum that you supply.

Note: `openmindR` will not automatically install all the packages necessary for each text tool because it is quite a lot and there are many dependencies. Instead, it will check whether the specified method is installed on your computer before it executes the code. If it's not, it asks you to install the relevant package. That way you only need to install what you actually use.

Arguments:

+ **`.data`** dataset including text and a personal identifier (must be named `OMID`)
+ **`method`** which method(s) should be applied? Currently supports: `"nrc"`, `"bing"`, `"afinn"`, `"textblob"`, `"vader"`, `"sentiment_stanford"`, `"sentimentr_polarity"`, `"affect3d"`, `"receptiveness"`, and `"toxicity"`.
+ **`text`** specify the text variable which should be scored

Here an example code that scores the free text from v7 with `bing`, `nrc` and `afinn` sentiment dictionaries.

```{r, eval = F}
assessmentv7 %>% 
 om_textscore(method = c("bing", "nrc", "afinn"), 
              text = IssueFreeTextPre) 
```


# openmindR ggplot2 theme

There are three functions for the ggplot2 theme:

+ `theme_om`
+ `scale_fill_om`
+ `scale_color_om`

Make sure you have the Poppins font installed!

```{r, eval = F}
extrafont::font_import()
```


```{r}
windowsFonts(`Poppins` = windowsFont("Poppins"))

```


[Good tutorial on how to install custom fonts in R](https://www.andrewheiss.com/blog/2017/09/27/working-with-r-cairo-graphics-custom-fonts-and-ggplot/)

**Example**

```{r fig.width=8, fig.height=5, message=F, warning=F, eval=T}
## Load tidyverse
library(tidyverse)

titanic_dat <- Titanic %>% as_tibble()

titanic_dat %>% 
  ggplot(aes(Sex, n)) +
  geom_col(aes(fill = Class), position = position_dodge()) +
  theme_om(legend_position = c(0.9, 0.75)) +
  scale_fill_om("Class") +
  facet_wrap(~Survived) +
  labs(title = "Titanic Survival by Age and Class") 
  
```

**Adapt `theme_om`**

+ `legend_position`
+ `axis_text_size`
+ `axis_title_size`
+ `legend_text_size`
+ `title_size`

```{r fig.width=8, fig.height=5, message=F, eval=T}
titanic_dat %>% 
  ggplot(aes(Class, n, fill = Class)) +
  geom_col() +
  theme_om(legend_position = "bottom",
           axis_text_size = 10,
           axis_title_size = 15, 
           legend_text_size = 10,
           title_size = 20) +
  scale_fill_om() +
  facet_wrap(~Survived) +
  labs(title = "Titanic Survival by Class") 
```

Or all text sizes at once

+ `overall_text_size`

```{r fig.width=8, fig.height=5, message=F, eval=T}
titanic_dat %>% 
  ggplot(aes(Class, n, fill = Class)) +
  geom_col() +
  theme_om(legend_position = "top",
           overall_text_size = 15) +
  scale_fill_om() +
  facet_wrap(~Survived) +
  labs(title = "Titanic Survival by Class") 
```


In case your pandoc is having problems check out this very neat fix:  https://github.com/rstudio/rstudio/issues/3661#issuecomment-475705806
